\documentclass[12pt,letterpaper]{article}
\usepackage{cv}

\begin{document}

\begin{center}
{\Large \textbf{TALON CHANDLER}}\\
{\textbf{CURRICULUM VIT\AE}}\\
\end{center}

\vspace{-1em}

\subsection*{Biographical Information}
\begin{itemize}[noitemsep]
\item[] \itab{Born:} \tab{June 24, 1993 in Calgary, Alberta}
\item[] \itab{Citizenship:} \tab{Canada}
\item[] \itab{Address:} \tab{655 Kansas Street}
\item[] \itab{} \tab{San Francisco, CA}
\item[] \itab{} \tab{94107}
\item[] \itab{Phone:} \tab{(415) 416-2831}
\item[] \itab{Email:} \tab{\texttt{talonchandler@talonchandler.com}}
\item[] \itab{Website:} \tab{\texttt{talonchandler.com}}
\item[] \itab{Core interests:} \tab{Image science, microscopy, fluorescence, polarized light,}
\item[] \itab{} \tab{experimental design, biological applications.}
\end{itemize}

\mysubsection{Current Position}
\begin{benumerate}{1}
  \item[] \textbf{Research and Development Engineer II} \hfill 2022--\\
  Advisor: Shalin Mehta \\
  Chan Zuckerberg Biohub, San Francisco
\end{benumerate}

\mysubsection{Education}
\begin{benumerate}{2}
\item
  \textbf{Ph.D. Medical Physics} \hfill 2020\\
  Dissertation: ``Spatio-angular fluorescence microscopy''\\
  Advisor: Patrick La Rivi\`ere \\
  University of Chicago
\item
  \textbf{B.A.Sc. Engineering Physics} \hfill 2015\\
  with electrical engineering specialization, with distinction\\
  GPA: 3.93/4.00\\
  University of British Columbia
\end{benumerate}

\mysubsection{Peer-Reviewed Publications}
\nocite{*}
\setlength\biblabelsep{0.035\textwidth}
\printbibliography[heading=none, type=article, sorting=ynt, resetnumbers=true]

\mysubsection{Peer-Reviewed Presentations}
\begin{benumerate}{12}
% Janelia talk

%% High throughput imaging and analysis of intracellular dynamics with correlative label-free and fluorescence microscopy

%% Ivan E. Ivanov, Eduardo Hirata-Miyasaki, Talon Chandler, Rasmi Cheloor-Kovilakam, Ziwen Liu, Chad Liu, Li-Hao Yeh, Juan A. Perez-Bermejo, Janie R. Byrum, James Y. S. Kim, Manuel D. Leonetti, Bo Huang, Shalin B. Mehta

\item {Sundarraman, D., \textbf{Chandler, T.}, Mehta, S. B., Balla, K., ``Mapping in toto \hfill 03/2024\\ immune cell dynamics during viral infection in zebrafish,'' American Physical\\ Society Meeting, Minneapolis, MN. 15 minute talk presented by Sundarraman, D.}

\item {\textbf{Chandler, T.}, Ivanov, I., Hirata-Miyasaki, E., Pradeep, S., Liu, Z., Foltz, C., \hfill 12/2023\\ Mehta, S. B., ``Physics-informed computation of label-free and fluorescence\\ microscopy data improves contrast, information content, and biophysical\\ interpretation,'' ASCB Cell Biology, Boston, MA. 15 minute talk.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 09/2019\\ La Rivi\`ere, P.J.,``3D and 4D computational imaging of molecular orientation\\ with multiview polarized fluorescence microscopy,'' Electronic Imaging Conference,\\ Burlingame, CA. 20 minute invited talk presented by La Rivi\`ere, P.J.}

\item {Oldenbourg, R., \textbf{Chandler, T.}, Tran, M., Guo, M., Shroff, H., La Rivi\`ere, P.J., \hfill 10/2019 ``Fast and comprehensive mapping of molecular orientation using multi-view\\polarized fluorescence microscopy,'' EMBL Seeing is Believing, Heidelberg, DE.\\ Poster presented by Oldenbourg, R.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 09/2019\\ La Rivi\`ere, P.J.,``Spatio-angular fluorescence imaging with a polarized\\ illumination light-sheet dual-view microscope,'' Junior Scientist Workshop on\\ Biological Optical Microscopy, Janelia Research Campus, VA. 20 minute talk.}

\item {\textbf{Chandler, T.}, La Rivi\`ere, P.J.,``Multipole spatio-angular fluorescence microscopy,'' \hfill 06/2019\\ Optics Society of America, Mathematics in Imaging, Munich, DE. 12 minute talk.\\ \textbf{Outstanding Student Presentation Award}}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 05/2019\\ La Rivi\`ere, P.J.,``Spatio-angular fluorescence imaging with a polarized\\ illumination light-sheet dual-view microscope,'' Frontiers in Imaging Science,\\ Janelia Research Campus, VA. Poster.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 04/2019\\ La Rivi\`ere, P.J., ``Spatio-angular fluorescence imaging with a polarized\\ illumination light-sheet dual-view microscope,'' Focus on Microscopy, London, UK.\\ 20 minute talk.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 02/2019\\ La Rivi\`ere, P.J., ``Spatio-angular imaging with a polarized light sheet dual-view\\ fluorescence microscope,'' Advanced Imaging Methods, Berkeley, CA. Poster.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 11/2018\\ La Rivi\`ere, P.J., ``Spatio-angular imaging with a polarized light sheet dual-view \\ fluorescence microscope,'' NSF Workshop on Enabling Biological Discovery\\ through Innovations in Imaging and Computation, Woods Hole, MA. Poster.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 06/2018\\ La Rivi\`ere, P.J., ``Spatio-angular restoration of fluorescence microscopy data,'' \\
      Optics Society of America, Mathematics in Imaging, Orlando, FL. 12 minute talk.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 06/2018\\ La Rivi\`ere, P.J., ``Spatio-angular restoration of fluorescence microscopy data,''\\
      Gordon Image Science Conference, Easton, MA. 15 minute talk and poster.}

\item {\textbf{Chandler, T.}, Guo, M., Kumar, A., Mehta, S., Shroff, H., Oldenbourg, R.,\hfill 04/2018\\ La Rivi\`ere, P.J., ``Single-fluorophore orientation determination with multiview\\ polarized
      illumination microscope,'' IEEE International Symposium on Biomedical\\ Imaging (ISBI), Washington, DC. Poster.}
\end{benumerate}

\mysubsection{Miscellaneous Presentations}
\begin{benumerate}{11}
  % Stanford course talk
\item {``Spatio-angular microscopy,'' \hfill 01/2024\\Berkeley Photobears optics club. 1 hour talk.}

\item {``Immediate computational microscopy,'' \hfill 09/2023\\Chan Zuckerberg Initiative make-a-thon tech talks. 30 minute talk.}

\item {``Anholonomy: falling cats, parallel parking, and polarized light,'' \hfill 01/2020\\Graduate Program on Medical Physics Journal Club. 30 minute talk.}

\item {``Spatio-angular fluorescence microscopy,'' \hfill 04/2019\\
     Graduate Program on Medical Physics Colloquium, Chicago, IL. 1 hour talk.}

\item {``Spatio-angular inverse problems in fluorescence microscopy,'' \hfill 03/2019\\
     Inverse Problems in Imaging Seminar, Chicago, IL. 1 hour talk.}

\item {``DNA microscopy,'' \hfill 03/2019\\
    Graduate Program on Medical Physics Journal Club. 30 minute talk.\\
    \textbf{Carl J. Vyborny Award for Best Journal Club Presentation}}

\item {``Are lenses necessary?'' \hfill 03/2018\\
    Graduate Program on Medical Physics Journal Club. 30 minute talk.\\
    \textbf{Carl J. Vyborny Award for Best Journal Club Presentation}}
  
\item {``Mapping molecular order in living organisms using polarized light microscopy,'' \hfill 10/2017\\
    with Rudolf Oldenbourg, University of California, Berkeley. 1 hour talk.}
  
\item {``Mapping molecular order in living organisms using polarized light microscopy,'' \hfill 10/2017\\
    with Rudolf Oldenbourg, SCIEN Colloquium, Stanford University. 1 hour talk.}
  
\item {``Evaluating gambles using dynamics,'' \hfill 04/2017\\
    Graduate Program on Medical Physics Journal Club. 30 minute talk.\\
    \textbf{Carl J. Vyborny Award for Best Journal Club Presentation}}

\item {``Digital holography for radiation dosimetry,'' \hfill 04/2016\\
    Graduate Program on Medical Physics Journal Club. 30 minute talk.}
\end{benumerate}

\mysubsection{Research History}
\begin{benumerate}{6}
\item
  {\textbf{Computational Microscopy Platform}, Chan Zuckerberg Biohub} \hfill 01/2021--11/2021\\
  Advisor: Shalin Mehta
\item
  {\textbf{Leslie Lab}, University of British Columbia} \hfill 01/2021--11/2021\\
  Advisor: Sabrina Leslie
\item
  {\textbf{La Rivi\`ere Lab}, University of Chicago} \hfill 09/2015--12/2020\\
  Advisor: Patrick La Rivi\`ere
\item
  {\textbf{Oldenbourg Lab}, Marine Biological Laboratory} \hfill 09/2017--09/2018\\
  Advisor: Rudolf Oldenbourg
\item
  {\textbf{MRI Research Centre}, University of British Columbia} \hfill 04/2014--09/2015\\
  Advisors: Alex MacKay \& Carl Michal
\item
  {\textbf{Centre For Operations Excellence}, University of British Columbia} \hfill 04/2013--09/2015\\
  Advisor: Steven Shechter
\end{benumerate}

\mysubsection{Employment History}
\begin{benumerate}{5}
\item
  \textbf{Chan Zuckerberg Biohub}, San Francisco, CA \hfill 03/2022--\\
  Research and Development Engineer II
\item
  \textbf{University of British Columbia}, Vancouver, BC \hfill 01/2021--11/2021\\
  Postdoctoral Scholar
\item
  \textbf{University of Chicago}, Chicago, IL \hfill 09/2015--12/2020\\
  Graduate Research Assistant
\item
  \textbf{Kardium Inc.}, Burnaby, BC \hfill 09/2013--12/2013\\
  Junior Engineer
\item
  \textbf{SRK Consulting Inc.}, Vancouver, BC \hfill 01/2012--04/2012\\
  Junior Engineer
\end{benumerate}

\mysubsection{Patents}
\begin{benumerate}{2}
  \item{Eng, P., Issa, N., La Rivi\`ere, P.J., \textbf{Chandler, T.}, Brickman, J., Proskey, M. \hfill 2021\\ ``Method and System for Mask Disinfection'', US\#326860. Pending. }
\item{Shroff, H., Kumar, A., Mehta, S., La Rivi\`ere, P.J., Oldenbourg, R., Wu, Y., \hfill 12/2020\\ \textbf{Chandler, T.}, ``Systems and methods for three-dimensional fluorescence\\ polarization via multiview imaging'', US\#16616891.}
\end{benumerate}

\mysubsection{Teaching}
\begin{benumerate}{4}
\item
  \textbf{Analytical and Quantitative Light Microscopy (AQLM)}, \hfill 2023\\
  Marine Biological Laboratory,\\
  Teaching Assistant

\item
  \textbf{Introduction to Medical Physics}, University of Chicago \hfill 2019\\
  Teaching Assistant\\
  Topics: Medical imaging and radiation therapy\\
  Rating: 4.7/5.0 from 11 students
\item
  \textbf{Medical Imaging 1}, University of Chicago \hfill 2017\\
  Teaching Assistant\\
  Topics: X-ray imaging, MRI, image restoration\\
  Rating: 5.0/5.0 from 5 students
\item
  \textbf{Mathematics For Medical Physics}, University of Chicago \hfill 2016\\
  Teaching Assistant\\
  Topics: Linear systems theory, stochastic processes, image reconstruction\\
  Rating: 4.8/5.0 from 5 students
\end{benumerate}

\mysubsection{Awards}
\begin{mybenumerate}{12}
\item \itab{Graduate Program on Medical Physics Best Dissertation Award} \rtab{\$500}\hfill{2021}
\item \itab{O'Brien--Hasten Research Collaboration Award} \rtab{\$1.5k}\hfill{2019}
\item \itab{University of Chicago Graduate Council Travel Award} \rtab{\$600}\hfill{2019}
\item \itab{University of Chicago Biological Sciences Division Travel Award} \rtab{\$500}\hfill{2019}
\item \itab{University of Chicago Biological Sciences Division Graduate Fellowship} \rtab{\$30k}\hfill{2016}
\item \itab{Eastern Irrigation District Graduate Scholarship} \rtab{\$2k}\hfill{2014}
\item \itab{NSERC Undergraduate Research Award} \rtab{\$4k}\hfill{2014}
\item \itab{NSERC Industrial Undergraduate Research Award} \rtab{\$4k}\hfill{2013}
\item \itab{Interpipeline Discovery Scholarship} \rtab{\$2k}\hfill{2011}
\item \itab{UBC President's Entrance Scholarship} \rtab{\$1.5k}\hfill{2010}
\item \itab{Alexander Rutherford Scholarship} \rtab{\$2.5k}\hfill{2010}
\item \itab{Junior Citizen of the Year, City of Brooks} \rtab{-}\hfill{2010}
\end{mybenumerate}

\mysubsection{Professional Membership}
\begin{mybenumerate}{4}
\item \itab{The Optical Society of America (OSA)} \hfill{2017--}
\item \itab{The International Society for Optics and Photonics (SPIE)} \hfill{2016--}
\item \itab{The American Association of Physicists in Medicine (AAPM)} \hfill{2015--2017}
\item \itab{Engineers \& Geoscientists of British Columbia (EGBC)} \hfill{2010--2016}
\end{mybenumerate}

\mysubsection{Reviewing}
19 total reviews
\begin{mybenumerate}{8}
\item \itab{Frontiers in Physics} \hfill{2023}
\item \itab{Journal of the Optical Society of America B} \hfill{2021}
\item \itab{European Biophysical Journal} \hfill{2019}
\item \itab{Optics Letters} \hfill{2019--2021}
\item \itab{Nature Communications} \hfill{2018--2023}
\item \itab{Optica} \hfill{2018}
\item \itab{Optics Express}  \hfill{2018--2023}
\item \itab{Journal of the Optical Society of America A} \hfill{2017--2022}
\end{mybenumerate}

\mysubsection{Computing}
\begin{itemize}[noitemsep]
\item[] \itab{\textbf{Top Language:}} \mtab{Python}
\item[] \itab{\textbf{Competent Languages:}} \mtab{C, \CPP, Bash, MATLAB}
\item[] \itab{\textbf{Familiar Languages:}} \mtab{R, Mathematica, HTML/CSS}
\item[] \itab{\textbf{Tools:}} \mtab{GNU Emacs, \LaTeX, git, VTK, ImageJ, SLURM}
\end{itemize}

\mysubsection{Other Activities}
\begin{itemize}[noitemsep]
\item[] \itab{\textbf{Ultramarathon running}} \mtab{12 races $\geq$ 26.2 miles}
\item[] \itab{\textbf{SCUBA diving}} \mtab{15 open water dives, $\sim$600 minutes underwater}
\item[] \itab{\textbf{Apiculture}}
\end{itemize}

% \mysubsection{References}
% \begin{itemize}[noitemsep]
% \item[] \itab{\textbf{Patrick La Rivi{\`e}re}} \mtab{\texttt{pjlarivi@uchicago.edu}} \hfill (773) 702-6975
% \item[] \itab{\textbf{Rudolf Oldenbourg}} \mtab{\texttt{rudolfo@mbl.edu}}\hfill (508) 289-7426
% \item[] \itab{\textbf{Hari Shroff}} \mtab{\texttt{hari.shroff@nih.gov}}\hfill (301) 435-1995
% \end{itemize}

\end{document}
